---
title: "ex vivo biopsy data"
author: "Toufic Mayassi"
date: "September 15, 2015"
output:
  html_document:
    fig_caption: yes
    fig_height: 6
    fig_width: 6
    highight: tango
    number_sections: yes
    self_contained: no
    theme: cosmo
    toc: yes
  pdf_document:
    toc: yes
  word_document: default
---

# importing/grooming data set

```{r}
library("dplyr")

biopsy_data <- read.csv("Data/IEL_PBL_frequency_data.csv", header = TRUE)

key3_subsets <- filter(biopsy_data, Disease_State == "Control" | Disease_State == "Active" | Disease_State == "GFD")

females <- filter(key3_subsets, Sex == "F")

males <- filter(key3_subsets, Sex == "M")

peds <- filter(key3_subsets, Age < 20)

adults <- filter(key3_subsets, Age > 20)

updated_stain <- filter(key3_subsets, Stain == "B" | Stain == "B1")

best_stainings <- filter(key3_subsets, Stain == "B")
```

# ggplot 2

```{r}
library("ggplot2")
```

# Total gd % in IEL 

```{r}
p <- ggplot(data = biopsy_data, mapping = aes(x = Disease_State,
                                           y = IEL)) + labs(title = "All TCRɣδ IEL", x = "", y = "% of CD3pos IEL") + geom_boxplot(notch = TRUE, notchwidth = .3, aes(color = Disease_State))
p
```

# Total gd % in IEL for key3_subsets

```{r}
p <- ggplot(data = key3_subsets, mapping = aes(x = Disease_State,
                                           y = IEL)) + labs(title = "TCRɣδ IEL", x = "", y = "% of CD3pos IEL") + geom_boxplot(notch = FALSE, notchwidth = .1, outlier.colour = "purple", outlier.size = 3, aes(color = Disease_State)) + geom_jitter()
p
```

# Total gd % in IEL with old staining method excluded

```{r}
p <- ggplot(data = updated_stain, mapping = aes(x = Disease_State,
                                           y = IEL)) + labs(title = "All TCRɣδ IEL", x = "", y = "% of CD3pos IEL") + geom_boxplot(notch = FALSE, notchwidth = .1, outlier.colour = "purple", outlier.size = 3, aes(color = Disease_State)) + geom_jitter()
p
```

# Total gd % in IEL with old staining method excluded and poor stains excluded(where cell numbers were too low to faithfully gate)

```{r}
p <- ggplot(data = best_stainings, mapping = aes(x = Disease_State,
                                           y = IEL)) + labs(title = "All TCRɣδ IEL", x = "", y = "% of CD3pos IEL") + geom_boxplot(notch = FALSE, notchwidth = .1, outlier.colour = "purple", outlier.size = 3, aes(color = Disease_State)) + geom_jitter()
p
```

# Total gd % in IEL Females 

```{r}
p <- ggplot(data = females, mapping = aes(x = Disease_State,
                                           y = IEL)) + labs(title = "TCRɣδ IEL Females", x = "", y = "% of CD3pos IEL") + geom_boxplot(notch = FALSE, notchwidth = .1, outlier.colour = "purple", outlier.size = 3, aes(color = Disease_State)) + geom_jitter()
p
```

# Total gd % in IEL Males

```{r}
p <- ggplot(data = males, mapping = aes(x = Disease_State,
                                           y = IEL)) + labs(title = "TCRɣδ IEL Males", x = "", y = "% of CD3pos IEL") + geom_boxplot(notch = FALSE, notchwidth = .1, outlier.colour = "purple", outlier.size = 3, aes(color = Disease_State)) + geom_jitter()
p
```

# Total gd % in IEL Peds

```{r}
p <- ggplot(data = peds, mapping = aes(x = Disease_State,
                                           y = IEL)) + labs(title = "TCRɣδ IEL Peds", x = "", y = "% of CD3pos IEL") + geom_boxplot(notch = FALSE, notchwidth = .1, outlier.colour = "purple", outlier.size = 3, aes(color = Disease_State)) + geom_jitter()
p
```

# Total gd % in IEL Adults

```{r}
p <- ggplot(data = adults, mapping = aes(x = Disease_State,
                                           y = IEL)) + labs(title = "TCRɣδ IEL Adults", x = "", y = "% of CD3pos IEL") + geom_boxplot(notch = FALSE, notchwidth = .1, outlier.colour = "purple", outlier.size = 3, aes(color = Disease_State)) + geom_jitter()
p
```

# Total gd % in PBL

```{r}
p <- ggplot(data = biopsy_data, mapping = aes(x = Disease_State,
                                           y = PBL)) + labs(title = "TCRɣδ PBL", x = "", y = "% of CD3pos PBL") + geom_boxplot(notch = TRUE, notchwidth = .3, aes(color = Disease_State))
p
```

# VD1 IEL % of GD 

```{r}
p <- ggplot(data = biopsy_data, mapping = aes(x = Disease_State,
                                           y = VD1_IEL_of_GD)) + labs(title = "Vδ1 IEL", x = "", y = "% of GDpos IEL") + geom_boxplot(notch = FALSE, notchwidth = .3, aes(color = Disease_State))
p
```

# VD2 IEL % of GD 

```{r}
p <- ggplot(data = biopsy_data, mapping = aes(x = Disease_State,
                                           y = VD2_IEL_of_GD)) + labs(title = "Vδ2 IEL", x = "", y = "% of GDpos IEL") + geom_boxplot(notch = FALSE, notchwidth = .3, aes(color = Disease_State))
p
```

# DN IEL % of GD 

```{r}
p <- ggplot(data = biopsy_data, mapping = aes(x = Disease_State,
                                           y = DN_IEL_of_GD)) + labs(title = "DN IEL", x = "", y = "% of GDpos IEL") + geom_boxplot(notch = FALSE, notchwidth = .3, aes(color = Disease_State))
p
```

# VD1 IEL % of CD3 

```{r}
p <- ggplot(data = biopsy_data, mapping = aes(x = Disease_State,
                                           y = VD1_IEL_of_CD3)) + labs(title = "Vδ1 IEL", x = "", y = "% of CD3pos IEL") + geom_boxplot(notch = TRUE, notchwidth = .3, aes(color = Disease_State))
p
```

# VD2 IEL % of CD3 

```{r}
p <- ggplot(data = biopsy_data, mapping = aes(x = Disease_State,
                                           y = VD2_IEL_of_CD3)) + labs(title = "Vδ2 IEL", x = "", y = "% of CD3pos IEL") + geom_boxplot(notch = TRUE, notchwidth = .3, aes(color = Disease_State))
p
```

# DN IEL % of CD3 

```{r}
p <- ggplot(data = biopsy_data, mapping = aes(x = Disease_State,
                                           y = DN_IEL_of_CD3)) + labs(title = "DN IEL", x = "", y = "% of CD3pos IEL") + geom_boxplot(notch = TRUE, notchwidth = .3, aes(color = Disease_State))
p
```
